\MakeUppercase{Graph Product Structure for Non-Minor-Closed Classes}

### 2022-03-11 k-planar.tex
more comments about improving to tw 3
added comments

\usepackage[longnamesfirst,numbers,sort&compress]{natbib}
\usepackage[noabbrev,capitalise]{cleveref}

@@

\crefname{lem}{Lemma}{Lemmas}
\crefname{thm}{Theorem}{Theorems}
\crefname{cor}{Corollary}{Corollaries}
\crefname{conj}{Conjecture}{Conjectures}
\crefname{obs}{Observation}{Observations}
\crefname{prop}{Proposition}{Propositions}
\crefname{clm}{Claim}{Claims}
\crefname{openproblem}{Open Problem}{Open Problems}
\crefformat{equation}{(#2#1#3)}
\Crefformat{equation}{Equation #2(#1)#3}

@@

\note{DW}{I think \cref{framed} should be proved explicitly and \cref{1-planar} should be a corollary, especially because \cref{NewMapGraph} is another corollary. This section should be about framed graphs, outside of \cref{sec-k-planar}. I suggest we make it a subsection of 
\cref{Structure} where we introduce framed graphs, say they can be described by $(2,\binom{d}{2})$-shortcut systems, so the main theorem is applicable, which gives a treewidth bound of $\binom{5}{3}-1=9$, but using  \cref{framed} we get a treewidth bound of 3, which is optional. Then in latter sections we give two applications, for 1-planar graphs and for $d$-map graphs. }

@@

@@

>>>>

\usepackage[longnamesfirst,numbers,sort&compress]{natbib}

\usepackage[noabbrev,capitalise]{cleveref}
\crefname{lem}{Lemma}{Lemmas}
\crefname{thm}{Theorem}{Theorems}
\crefname{cor}{Corollary}{Corollaries}
\crefname{prop}{Proposition}{Propositions}
\crefname{conj}{Conjecture}{Conjectures}
\crefname{open}{Open Problem}{Open Problems}
\crefname{claim}{Claim}{Claims}
\crefname{enumi}{Item}{Items}
\crefname{obs}{Observation}{Observations}
\crefname{clm}{Claim}{Claims}
\crefname{openproblem}{Open Problem}{Open Problems}
\crefformat{equation}{(#2#1#3)}
\Crefformat{equation}{Equation #2(#1)#3}

@@

@@

\note{DW}{I think \cref{framed} should be proved explicitly and \cref{1-planar} should be a corollary, especially because \cref{NewMapGraph} is another corollary. The proof of \cref{framed} needs an extra clause; see the last sentence of \cref{NewLemma}. This section should be about framed graphs, outside of \cref{sec-k-planar}. I suggest we make it a subsection of \cref{Structure} where we introduce framed graphs, say they can be described by $(2,\binom{d}{2})$-shortcut systems, so the main theorem is applicable, which gives a treewidth bound of $\binom{5}{3}-1=9$, but using  \cref{framed} we get a treewidth bound of 3, which is optional. Then in latter sections we give two applications, for 1-planar graphs and for $d$-map graphs. }

@@

\note{DW}{We should be able to get treewidth 3 for $(g,1)$-planar graphs, combining the method in \cref{1-planar} with \citep{DHHW}}

@@

\note{DW}{We should be able to get treewidth 3 here using \cref{framed} and \citep{DHHW}.}
